My title

### 2024-04-18 paper/paper.qmd
model data added and other changes made

library(tidyverse)
library(ggplot2)

@@

@@

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

@@

@@

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

# Appendix {-}

>>>>

library(tidyverse)
library(ggplot2)
library(modelsummary)

@@

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
analysis_data$IHDI <- round(as.numeric(analysis_data$IHDI), 3)

# View the changes to ensure they have been applied
head(analysis_data$IHDI)

@@

@@

```{r}
#| label: scat-hap-ihdi
#| fig-cap: Relationship between IHDI and Happiness
#| echo: false

# Scatter plot between IHDI and Happiness Score
# Load the necessary library
library(ggplot2)

# Assuming analysis_data is your data frame and it has 'IHDI' and 'Happiness_Score' columns
# Basic scatter plot for IHDI vs. Happiness Score
basic_plot_ihdi <- ggplot(analysis_data, aes(x = IHDI, y = Happiness_score)) +
  geom_point()

# Display the plot
print(basic_plot_ihdi)

@@

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

first_model <-
  readRDS(file = here::here("models/first_model.rds"))

second_model <-
  readRDS(file = here::here("models/second_model.rds"))

```{r}
#| echo: false
#| eval: true
#| label: tbl-secondtmodelresults
#| tbl-cap: "Multiple Linear Regression"
#| warning: false

# Generate the model summary for 'first_model' with the desired statistics
modelsummary::modelsummary(
  list(
    "Second model" = second_model
  ),
  statistic = c("std.error", "statistic", "p.value", "conf.int")
)
```

@@

# Appendix {.unnumbered}
